Generate data for multispecies modeling, including diet!

### 2020-10-21 NOBAmsdiets.Rmd
agecomp and wtage--Blue whiting age comps problem?

Also need new plot functions and updated input file-writing functions that expect this structure.

@@

#### Survey age composition (age classes)
```{r agecomp-1, eval=FALSE}

@@

Natageplot <- <- function(dat){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
}

@@

#### Survey weight at age (age classes)
```{r wtageclass-1, eval=FALSE}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]]

wageplot + facet_wrap(c("species"), scales="free_y")
```

@@

#### Fishery age composition (age classes)
```{r fishagecomp-1, eval=FALSE}

@@

Natage <- filter(fish_age_comp, time %in% c(30:53))

  Natageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

>>>>

Also need new plot functions and updated input file-writing functions that expect this structure. Preliminary plot functions below.

@@

#### Survey age composition (age classes)
```{r agecomp-1}

@@

Natageplot <- function(dat){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
}

@@

##### `r names(age_comp_data)[1]`
``` {r}
acompsub <- as.data.frame(age_comp_data$BTS_spring_allbox_effic1[1]) %>% filter(time %in% c(150:270)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)

for(i in 1:length(acompsub)) {
  print(acompsub[[i]])
}
```

##### `r names(age_comp_data)[2]`
``` {r}
acompsub <- as.data.frame(age_comp_data$BTS_spring_allbox_effic1[1]) %>% filter(time %in% c(150:270)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)

for(i in 1:length(acompsub)) {
  print(acompsub[[i]])
}
```

#### Survey weight at age (age classes)
```{r wtageclass-1}

# now done with function above
# wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
# wtage <- wtage[[1]]

wageplot <- function(dat){
  ggplot(dat, aes(time, atoutput)) +
    geom_line(aes(colour = factor(agecl))) +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("model timestep (5 per year)") +
    ylab("average individual weight (g)") +
    labs(subtitle = paste0(scenario.name)) +
    facet_wrap(c("species"), scales="free_y")
}

#wageplot 
```

##### `r names(wtage)[1]`
``` {r}
map(wtage$BTS_fall_allbox_effic1, wageplot)[[1]]
```

##### `r names(wtage)[2]`
``` {r}
map(wtage$BTS_spring_allbox_effic1, wageplot)[[1]]
```

@@

#### Fishery age composition (age classes)
```{r fishagecomp-1}

@@

acompsub <- as.data.frame(age_comp_data$BTS_spring_allbox_effic1[1]) %>% filter(time %in% c(150:270)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)

for(i in 1:length(acompsub)) {
  print(acompsub[[i]])
}
